Pillar 1 - Student Topic Profile

### 2019-03-25 Pillar 1 - Topic Profile.Rmd
Best subset selection to identify prerequisite topics for each course
Lasso is consider but has important drawbacks

library(tidyverse)
library(magrittr)
```

@@

```{r}
gamma <- topic_model_gb$g_overview[[10]] %>% spread(topic, gamma)
```

@@

  left_join(gamma, by = c("Course ID" = "document")) %>%
  filter(!is.na(`Topic 1`)) %>%

@@

```{r}
d_transcript_cum %>%

@@

>>>>

library(tidyverse)
library(magrittr)
library(glmnet)
library(leaps)
```

@@

```{r}
gamma        <- topic_model_gb$g_overview[[10]] %>% mutate(topic = topic %>% str_replace(" ", "_"))
gamma_spread <- gamma %>% spread(topic, gamma)
```

@@

  left_join(gamma_spread, by = c("Course ID" = "document")) %>%
  filter(!is.na(`Topic_1`)) %>%

@@

```{r}
d_TP_cum <- d_transcript_cum %>%

  right_join(d_transcript_informative, by = c("sequenceID" = "Student ID", "eventID" = "time")) %>%

@@

```{r}
course_all <- unique(d_transcript_informative$`Course ID`)
course_obj <- course_all[! course_all %>% str_detect("^...10")]

find_prep <- function(objective){

  data_temp <- d_TP_cum %>%

    filter(`Course ID` == objective) %>%

    select(Grade, matches("Topic"))

  if(nrow(data_temp) <= 7) return(NULL)

  #
  # best subset selection
  m <- regsubsets(Grade ~ ., data_temp, nvmax = 6)

  coefi <- coef(m, 6)[-1]  # check that 6 is usually a good subset size

  tibble(topic = names(coefi), weight = coefi) %>%

    right_join(gamma, by = "topic") %>%

    mutate(weight = weight %>% replace_na(0)) %>%

    # double prep_score of intro courses
    mutate(is_intro = document %>% str_detect("^...10")) %>%
    mutate(weight = weight * (1 + is_intro)) %>%

    group_by(document) %>%
    summarize(prep_score = sum(weight * gamma)) %>%
    mutate(objective = objective) %>%

    arrange(desc(prep_score)) %>%

    filter(! document %>% str_detect("^...30")) %>%
    filter(document %in% course_all) %>%

    top_n(10, prep_score)

}

results <- course_obj %>% map(find_prep) %>% bind_rows
View(results)
```

```{r}
#
# lasso (instead of best subset selection due to the large number of predictors (number of topics))
# disadvantage: difficult to estimate lambda a-priori
x <- model.matrix(Grade ~ ., test)[ , -1]
y <- test$Grade
lambda <- 10^seq(-0.1, -2, length = 14)

results <- glmnet(x, y, alpha = 1, lambda = lambda)
coef(results)

# first positive coefficient is topic 5. Topic 3 and 19 appear a little later.
results$lambda
```
